---
title: "STAT 385 Statistics Programming Methods - Spring 2021"
output: html_document
---

## Homework 03
### Due: Monday March 08, 2021 11:59 pm US Central Time
#### Created by Course staff

Grading Rubric (per question):  
2 points if complete and correct  
1 point if incomplete or incorrect  
0 points if no attempt made  


**Retrieving your work**

This and all future homework .Rmd files are written in RMarkdown. The .Rmd file is rendered as an .html file for easier viewing. This and all future homework assignments are located in the **homework** directory within the **stat385-sp21-course-content** repo, i.e. **stat385-sp21-course-content/homework** in GitHub. It is always recommended that you **pull** (or refresh) the **stat385-sp21-course-content** repo to ensure that you have the most updated version of all course content including the homework assignments. After pulling (or refreshing) the **stat385-sp21-course-content** repo, the homework file will be in the homework directory. 

**Submitting your work**

In your individual student repo (named as your netID), you are to submit ***two*** files:

a. Your reproducible document file (.Rmd) which should be saved as homework##-netID.Rmd. For example, my homework 01 file would be saved as homework01-kinson2.Rmd.

b. Your rendered reproducible document file (.html) which should be saved as homework##-netID.html. For example, my homework 01 file would be saved as homework01-kinson2.html.

You have an unlimited number of submissions, but only the latest proper submission (commit and push) will be viewed and graded. **Remember the .Rmd file needs to render properly to .html before submitting.** 


***

Students are expected to complete all problems.

*The following problems should be completed by you as an individual. If any problem asks you a particular question, be sure to answer it completely (with code, written sentences, or both). Written sentences should not appear in code chunks or code cells. Written sentences should appear in Markdown syntax unless specifically stated otherwise.*

***Do not change anything in this file above the double line.***

***
***

### Use only R and RMarkdown for this entire homework assignment. Use the URLs to access the data (if any). No local files allowed. Functions or programming ideas beyond the topics/ideas covered thus far are not allowed. The `subset` function is never allowed in this course.

**#1** (Markdown) Using Markdown syntax, make a numbered list with your first name in normal text as the first item and your last name in italic text as the second item.

1. Yeonchul
2. *Choi*

**#2** (Personal survey, Markdown) Think about the previous two weeks (your experiences, assignments, life). Using Markdown, describe in paragraph form (with at least 3 complete sentences) what was the most challenging part(s) about homework 02, the most challenging part(s) about your weeks 03-04, and the thing(s) that made your weeks successful or unsuccessful.

-By working on homework 02 I learned how to use matrix in the R. And I didn't know the paste0 function in R that paste the value without spaces. And I learned about pull request that I didn't know before.

**#3** (Introduction to R Chapter 6, Tibbles, Markdown) A **tibble** is a kind of data frame and a data frame is a kind of list. If the text in bold is the term that makes the statement true, then write TRUE below in all caps. If the text in bold is the term that makes the statement false, then write FALSE below in all caps and write the correct term in bold text in a new line under FALSE.

-TRUE

**#4** (Introduction to R Chapter 2, Introduction to R Chapter 10) Create one custom user-defined function to determine if the numbers 1211 and 1217 are composite or not. *Recall, a number, X, is composite if it is divisible by a different number other than 1 and itself.* **Your function must be your own and not an existing prime number function.**

```{r}
composite = function(x){
  y = 0
  z = x/2
  for (i in 2:z){
    if (x%%i==0)
      y=1
    if (x==1)
      y=0
    if (x==2)
      y=0
  }
  if (y==1)
    print(paste("Composite"))
  else
    print(paste("Not Composite"))}
```

```{r}
composite(1211)
composite(1217)
```

**#5** (Introduction to R Chapter 2, Introduction to R Chapter 10) Create one custom user-defined function to convert 13 imperial liquid cups to cubic feet.

```{r}
convert = function(x){
  y=x*0.010033
  print(y)
}
```
```{r}
convert(13)
```

**#6** (Introduction to R Chapter 5, Introduction to R Chapter 8) Create a matrix (named as `matrix01`) with three columns such that column 1 contains the last 10 capitalized letters of the alphabet in repeating sequence (i.e. Q, Q, R, R, ..., Z, Z), column 2 contains 20 random continuous t distribution deviates (where the degrees of freedom is 15) rounded to the hundredths place, and column 3 contains a randomized ordering of the concatenated values of columns 1 and 2. Print the resulting `matrix01`. *The concatenation should not have any spaces between the values of columns 1 and 2. For example, the concatenated values might appear as "Q1.5". There should be only 20 rows in `matrix01`.* 

```{r}
col1_6 = rep(LETTERS[17:26],2)
col1_6 = sort(col1_6, decreasing =FALSE)

col2_6 = rt(20,15)
col2_6 = round(col2_6, 2)

col3_6 = paste0(col1_6, col2_6)
col3_6 = sample(col3_6)

matrix01 = cbind(col1_6,col2_6,col3_6)
matrix01
```


**#7** (Introduction to R Chapter 6, Introduction to R Chapter 8) Create a data frame (named as `df01`) with three columns such that column 1 contains the last 10 capitalized letters of the alphabet in repeating sequence (i.e. Q, Q, R, R, ..., Z, Z), column 2 contains 20 positive random continuous t distribution deviates (where the degrees of freedom is 15) rounded to the hundredths place, and column 3 contains a randomized ordering of the concatenated values of columns 1 and 2. *The concatenation should have a '+' sign between the values of columns 1 and 2. For example, the concatenated values might appear as "Q+1.5". There should be only 20 rows in `df01`.*  

```{r}
col1_7 = col1_6
col2_7 = abs(rt(20,15))
col2_7 = round(col2_7, 2)

col3_7 = paste0(col1_7, "+", col2_7)
col3_7 = sample(col3_7)

df01 = data.frame(col1_7, col2_7, col3_7)
df01
```

**#8** (Introduction to R Chapter 5, Introduction to R Chapter 6, Tibbles, Markdown) Write a list using Markdown syntax that contains 1 advantage and 1 disadvantage to using data frames instead of matrices.

Advantage: We can use different type of data in each column when we use data frame, but in a matrix, we can only use same type of data.
Disadvantage: Matrix is more memory efficient than data frame and we can use many arithmetic operations.

**#9** (Introduction to R Chapter 6, Tibbles, Markdown) Write a list using Markdown syntax that contains 1 advantage and 1 disadvantage to using lists instead of data frames.

Advantage: In data frames, all the elements should be vectors but in list, all the elements must not be vectors.
Disadvantage: We can select rows and make operations on each rows in data frame but in list we can make operations because each row is not defined.

**#10** (Introduction to R Chapter 6, Introduction to R Chapter 8, Introduction to R Chapter 10, Tibbles) Create a custom user-defined function that returns a shuffled deck of standard playing cards (52 cards total). The deck must be a tibble such that the first column stores the "Face" about the face value of the card, the second column stores the "Suit" about the suit of the card, third column stores the "Color" about the suit's color, and the fourth column stores the "Points" about the numeric point value of each card. Show the result of using your user-defined function. *The face of a card is the number or any of the royal members. Aces are 14 points, Kings are 13 points, Queens are 12 points, and Jacks are 11 points.* Read the [Composition section on Wikipedia](https://en.wikipedia.org/wiki/Standard_52-card_deck) for more details about the standard 52-card deck.

```{r}
library(tibble)

face = rep(c("A",2:10,"J","Q","K"),4)

suit = c(rep("spade",13),rep("diamond",13),rep("heart",13),rep("club",13))

color = c(rep("black",13),rep("red",13),rep("red",13),rep("black",13))

point = rep(c(14,2:10,11,12,13),4)

cards=tibble(face=face, color=color, suit=suit, point=point)
shuffle=function(data){
  data[sample(1:52), ]
}
shuffle(cards)
```
