---
title: "STAT 385 Statistics Programming Methods - Spring 2021"
output: html_document
runtime: shiny
---

## Homework 06
### Due: Monday April 26, 2021 11:59 pm US Central Time
#### Created by Course staff

Grading Rubric (per question):  
2 points if complete and correct  
1 point if incomplete or incorrect  
0 points if no attempt made  


**Retrieving your work**

This and all future homework .Rmd files are written in RMarkdown. The .Rmd file is rendered as an .html file for easier viewing. This and all future homework assignments are located in the **homework** directory within the **stat385-sp21-course-content** repo, i.e. **stat385-sp21-course-content/homework** in GitHub. It is always recommended that you **pull** (or refresh) the **stat385-sp21-course-content** repo to ensure that you have the most updated version of all course content including the homework assignments. After pulling (or refreshing) the **stat385-sp21-course-content** repo, the homework file will be in the homework directory. 

**Submitting your work**

In your individual student repo (named as your netID), you are to submit ***two*** files:

a. Your reproducible document file (.Rmd) which should be saved as homework##-netID.Rmd. For example, my homework 01 file would be saved as homework01-kinson2.Rmd.

b. Your rendered reproducible document file (.html) which should be saved as homework##-netID.html. For example, my homework 01 file would be saved as homework01-kinson2.html.

You have an unlimited number of submissions, but only the latest proper submission (commit and push) will be viewed and graded. **Remember the .Rmd file needs to render properly to .html before submitting.** 


***

Students are expected to complete all problems.

*The following problems should be completed by you as an individual. If any problem asks you a particular question, be sure to answer it completely (with code, written sentences, or both). Written sentences should not appear in code chunks or code cells. Written sentences should appear in Markdown syntax unless specifically stated otherwise.*

***Do not change anything in this file above the double line.***

***
***

### Use only R and RMarkdown for this entire homework assignment. Use the URLs to access the data (if any). No local files allowed. Functions or programming ideas beyond the topics/ideas covered thus far are not allowed. The `subset` function is never allowed in this course.

**#1** (Markdown) Using Markdown syntax, make a numbered list with your first name in normal text as the first item and your last name in italic text as the second item.

1. Yeonchul
2. *Choi*

**#2** (Personal survey, Markdown) Think about the previous two weeks (your experiences, assignments, life). Using Markdown, describe in paragraph form (with at least 3 complete sentences) what was the most challenging part(s) about the homework 05, the most challenging part(s) about your weeks 10-11, and the thing(s) that made your weeks successful or unsuccessful.

The most challenge for last two weeks was on HW 5 question 9 and 10 which makes UNO. It was really hard to make new function of UNO playing cards.

**#3** (Parallel programming, Markdown) The `foreach` operation, **`%dopar%`**, evaluates an expression sequentially. If the text in bold is the term that makes the statement true, then write TRUE below in all caps. If the text in bold is the term that makes the statement false, then write FALSE below in all caps and write the correct term in bold text in a new line under FALSE.

**`%do%`**

**#4** (Parallel programming, Markdown) Select the scenario(s) that are appropriate for using parallel programming. There may be more than one scenario that is appropriate. To select an answer, place an x within the brackets as `[x]`.

- [x] computer has more than 1 core or more than 1 processor

- [ ] code cannot be made into independent repetitive chunks

- [x] large-scale computational needs

- [ ] sequential code takes microseconds to run on a single computer

**#5** (Shiny app) Using Shiny, make a histogram with the `faithful` data. Allow the user to change the number of observations for the waiting column. **You should create a code chunk which will correctly run the Shiny app. The faithful dataset is an internal dataset in R which can be accessed with the R code: `faithful` in your R console.**

```{r}
ui = fluidPage(
  sliderInput(inputId = "size",
              label = "Number of observations:",
              min = 1,
              max = nrow(faithful)[1],
              value = floor(nrow(faithful)[1]/2)),
  
  plotOutput(outputId="Q5_hist")
)

server = function(input,output) {
  dat = reactive({
    sample(faithful$waiting,input$size,replace=FALSE)})
  output$Q5_hist = renderPlot({
    hist(dat(),main="Question 5",col='darkblue')})
}

shinyApp(ui=ui,server=server,options = list(height = 500))
```

**#6** (Shiny app) Using Shiny, make a histogram for the eruptions column of the `faithful` data. Allow the user to change the number of observations for the eruptions column. **You should create a code chunk which will correctly run the Shiny app. The faithful dataset is an internal dataset in R which can be accessed with the R code: `faithful` in your R console.**

```{r}
ui = fluidPage(
  sliderInput(inputId = "size",
              label = "Number of observations:",
              min = 1,
              max = nrow(faithful)[1],
              value = floor(nrow(faithful)[1]/2)),
  
  plotOutput(outputId="Q6_hist")
)

server = function(input,output) {
  df = reactive({
    sample(faithful$eruptions,input$size,replace=FALSE)})
  output$Q6_hist = renderPlot({
    hist(df(),main="Question 6",col='darkblue')})
}

shinyApp(ui=ui,server=server, options = list(height = 500))
```

**#7** (Shiny app) Using Shiny, make a scatter plot with the `faithful` data. **The faithful dataset is an internal dataset in R which can be accessed with the R code: `faithful` in your R console.** Allow the user to change the number of observations for both x (eruptions) and y (waiting) variables simultaneously with one slider. **You should create a code chunk which will correctly run the Shiny app.**

```{r}
ui = fluidPage(
  sliderInput(inputId = "size",
              label = "Number of observations:",
              min = 1,
              max = nrow(faithful)[1],
              value = floor(nrow(faithful)[1]/2)),
  
  plotOutput(outputId="Q7_scatter")
)

server = function(input,output) {
  df = reactive({
    sample(1:nrow(faithful)[1],input$size,replace=FALSE)})
    
  output$Q7_scatter = renderPlot({
    plot(faithful$eruptions[df()],faithful$waiting[df()],
         col='darkblue',pch=16,main="Question 7")
    })
}

shinyApp(ui=ui,server=server,options = list(height = 500))
```

**#8** (Shiny app) Create a magic 8 ball Shiny app. The user must ask a yes or no question in a text box and click a button to submit the question to the 8 ball. The 8 ball must respond randomly with one of 20 possible answers. See https://en.wikipedia.org/wiki/Magic_8-Ball for the 20 possible answers. Additionally, you must add an image of the 8 ball to the shiny app. The image serves as something nice to look at. **You should create a code chunk which will correctly run the Shiny app.**

```{r}
ui = fluidPage(
  textInput(inputId = "selection",
              label = "Yes or No question?"),
  
  actionButton(inputId="clicks",
               label="Submit"),
  htmlOutput(outputId = "img"),
  verbatimTextOutput(outputId="msg")
)

server = function(input,output) {
  observeEvent(input$clicks,{
    src = c("<img src=https://static.coolgift.com/media/cache/sylius_shop_product_large_thumbnail/product/Magic-8-Ball-102.jpg width=500px,height=500px>")
    indx = sample(1:20,1)
    s = switch(indx,
               "1" = "It is certain.",
               "2" = "It is decidedly so.",
               "3" = "Without a doubt.",
               "4" = "Yes – definitely.",
               "5" = "You may rely on it.",
               "6" = "As I see it, yes.",
               "7" = "Most likely.",
               "8" = "Outlook good.",
               "9" = "Yes.",
               "10" = "Signs point to yes.",
               "11" = "Reply hazy, try again.",
               "12" = "Ask again later.",
               "13" = "Better not tell you now.",
               "14" = "Cannot predict now.",
               "15" = "Concentrate and ask again.",
               "16" = "Don't count on it.",
               "17" = "My reply is no.",
               "18" = "My sources say no.",
               "19" = "Outlook not so good.",
               "20" = "Very doubtful.")
    output$msg = renderPrint({s})
    output$img = renderText({src})
  })
}

shinyApp(ui=ui,server=server,options = list(height = 500))
```

**#9** (Shiny app) There's something not quite right about the code in the following Shiny app. Identify what's the problem and explain it in Markdown syntax. **The `library(shiny)` is not the problematic part.**
We need to use reactive function because we have to make our data by rnorm in both summary and histogram.
```{r eval=FALSE}
#this code is not quite right
#library(shiny)
ui <- fluidPage(
  
  # Sidebar with a slider input for number of bins 
  sliderInput(inputId = "size",
              label = "Number of observations:",
              min = 1,
              max = 1e6,
              value = 30), #the comma is important
  
  # Make space for a plot of the generated distribution
  plotOutput(outputId = "histPlot"),
  
  # Make space for a summary table
  verbatimTextOutput(outputId = "sumtable")
)

# Define server logic
server <- function(input, output) {
  
  output$histPlot <- renderPlot({
    
    # draw the histogram plot
    hist(rnorm(input$size), col = 'darkgray', xlab="", main="Normal Distribution")
  })
  
  # print table of summary statistics
  output$sumtable <- renderPrint({
    summary(rnorm(input$size))
  })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

**#10** (Shiny app) Based on **Problem 9**, we know there's something not quite right about the following Shiny app and its code. Fix the code such that the Shiny app work properly. **You should create a separate code chunk which will correctly run the Shiny app. The `library(shiny)` is not the problematic part.**

```{r}
#this code is not quite right
#library(shiny)

ui <- fluidPage(
  
  # Make Sidebar with a slider input for number of bins 
  sliderInput(inputId = "size",
              label = "Number of observations:",
              min = 1,
              max = 1e6,
              value = 30), #the comma is important
  
  # Make space for a plot of the generated distribution
  plotOutput(outputId = "histPlot"),
  
  # Make space for a summary table
  verbatimTextOutput(outputId = "sumtable")
)

# Define server logic
server <- function(input, output) {
  df = reactive({
    rnorm(input$size)})
  output$histPlot <- renderPlot({
    
    # draw the histogram plot
    hist(df(), col = 'darkgray', xlab="", main="Normal Distribution")
  })
  
  # print table of summary statistics
  output$sumtable <- renderPrint({
    summary(rnorm(input$size))
  })
}

# Run the application 
shinyApp(ui = ui, server = server)
```
