---
title: "STAT 385 Statistics Programming Methods - Spring 2021"
author: Yeonchul Choi
output: html_document
---

## Homework 01 
### Due: Monday February 08, 2021 11:59 pm US Central Time
#### Created by Course staff

Grading Rubric (per question):  
2 points if complete and correct  
1 point if incomplete or incorrect  
0 points if no attempt made  


**Retrieving your work**

This and all future homework .Rmd files are written in RMarkdown. The .Rmd file is rendered as an .html file for easier viewing. This and all future homework assignments are located in the **homework** directory within the **stat385-sp21-course-content** repo, i.e. **stat385-sp21-course-content/homework** in GitHub. It is always recommended that you **pull** (or refresh) the **stat385-sp21-course-content** repo to ensure that you have the most updated version of all course content including the homework assignments. After pulling (or refreshing) the **stat385-sp21-course-content** repo, the homework file will be in the homework directory. 

**Submitting your work**

In your individual student repo (named as your netID), you are to submit ***two*** files:

a. Your reproducible document file (.Rmd) which should be saved as homework##-netID.Rmd. For example, my homework 01 file would be saved as homework01-kinson2.Rmd.

b. Your rendered reproducible document file (.html) which should be saved as homework##-netID.html. For example, my homework 01 file would be saved as homework01-kinson2.html.

You have an unlimited number of submissions, but only the latest proper submission (commit and push) will be viewed and graded. **Remember the .Rmd file needs to render properly to .html before submitting.** 


***

Students are expected to complete all problems.

*The following problems should be completed by you as an individual. If any problem asks you a particular question, be sure to answer it completely (with code, written sentences, or both). Written sentences should not appear in code chunks or code cells. Written sentences should appear in Markdown syntax unless specifically stated otherwise.*

***Do not change anything in this file above the double line.***

***
***

### Use only R and RMarkdown for this entire homework assignment. Use the URLs to access the data (if any). No local files allowed. Functions or programming ideas beyond the topics/ideas covered thus far are not allowed. The `subset` function is never allowed in this course.

**#1** (Markdown) Using Markdown syntax, make a numbered list with your first name in normal text as the first item and your last name in italic text as the second item.


1. Yeonchul
2. *Choi*


**#2** (Personal survey, Markdown) Select all of the following that you feel are must-haves in order for your learning to be successful.

i. lecture videos  
ii. course notes  
iii. assignments  
iv. assignment solutions  
v. feedback on the assignments  
vi. office hours  
vii. discussions with classmates

All of them

**#3** (Personal survey, Markdown) What is the highest numbered STAT course you have taken prior to this semester? *For example, STAT 510 is higher than STAT 480.* 

STAT 432

**#4** (Syllabus, Markdown) All assignments are assumed to be in which time zone? 

All assignments are assumed to be in CST which is time zone of Illinois.

Any and all times listed in this document are in current US Central Time

**#5** (Syllabus, Markdown) In an unordered list, write the names of the course staff.

-Christopher Kinson

-Michael Wieck-Sosa

-Yuriy Kotskyy

**#6** (RMarkdown, Simple manipulations, Numbers and vectors) Determine if these numbers are prime or not using vectors, sequences, and operators. *Recall, a number, X, is prime if it is only divisible by 1 and itself.*

```{r}
prime<- function(n){
  dev <- n/2
  prime <- T
  for( i in 2:dev) {
    if(n %% i == 0)
        prime <- FALSE
  }
    if(prime) print(paste("Prime Number"))
    else print(paste("Composite Number"))
}

prime(1211)
prime(1217)
```
a. 1211
Composite Number
b. 1217
Prime Number  


**#7** (RMarkdown, Simple manipulations, Numbers and vectors) Reproduce the result using vectors, sequences, and no more than one additional base R function. Using `c()` and `seq()` are allowed in addition to the one base R function. This one base R function could be used multiple times. *The shape, height, and width of the result do not matter.*

``` 
"covid-01"  "covid-02"  "covid-03"  "covid-04"  "covid-05" 
"covid-06"  "covid-07"  "covid-08"  "covid-09"  "covid-10"
"covid-11"  "covid-12"  "covid-13"  "covid-14"  "covid-15" 
"covid-16"  "covid-17"  "covid-18"  "covid-19"
```
```{r}
a <- seq(1,19)
sprintf("covid-%02d", a)
```

**#8** (RMarkdown, Simple manipulations, Numbers and vectors) Using the vector `X` within the code `set.seed(385); X <- rnorm(10)` compute the following statistics for `X` using the formulas as a guide. *No functions are allowed.*  
```{r}
set.seed(385)
x=rnorm(10)
x
#mean
x_bar= (0.88745254 + 1.13788102 - 0.38303588 - 0.60017263 - 0.79764060 - 0.61346699 + 0.77728575 - 0.03958418 + 0.44064853 + 0.75416090)/10
x_bar
```
```{r}
(x-x_bar)^2
s=(0.53450677 + 0.96339756 + 0.29094020 + 0.57233080 + 0.91010349 + 0.59262259 + 0.38555767 + 0.03839132 + 0.08082404 + 0.35737447)/9
s
```
a. sample mean $\bar{x}=\frac{1}{N}\sum_{i=1}^{N} x_i$   
0.1563528

b. sample variance $s=\frac{1}{N-1}\sum_{i=1}^{N}(x_i-\bar{x})^2$  
0.5251165


**#9** (RMarkdown, Simple manipulations, Numbers and vectors) Using the vector `X` within the code `set.seed(385); X <- rnorm(10)` compute the following statistics for `X` using the formulas as a guide. *The functions `length()`, `mean()`, and `sum()` are allowed; no other functions.*
```{r}
set.seed(385)
x=rnorm(10)
mean(x)
```
```{r}
sum((x-mean(x))^2)/(length(x)-1)
```
a. sample mean $\bar{x}=\frac{1}{N}\sum_{i=1}^{N} x_i$   
0.1563528    
b. sample variance $s=\frac{1}{N-1}\sum_{i=1}^{N}(x_i-\bar{x})^2$   
0.5251165


**#10** (RMarkdown, Simple manipulations, Numbers and vectors) Using the mortgage calculation formula, determine the value of someone's original home price in US Dollars, $h$, where:151036.9

$$ n = \frac{\mathrm{ln} \left( \frac{r}{\frac{m}{p} - r} + 1 \right)}{\mathrm{ln}(1 + r)}$$

- $n=360$: number of mortgage payment terms.  
- $m=610$: the monthly payment amount (US Dollars).  
- $p=?$: the loan amount (US Dollars).  
- $r=0.0034375$: the monthly interest rate.  
- $h=d+p$: the original home price (US Dollars).  
- $d=0.2\cdot p$: down payment (US Dollars). 

```{r}
n=360
m=610
r=0.0034375
m/((r/(((1+r)**n-1)))+r)
p=m/((r/(exp(n*log(1+r))-1))+r)
d=0.2*p
h=d+p
h
```
